Improving Software Maintainability through Automated Refactoring of Code Clones

### 2019-08-13 icse/paper.tex
Refactoring techniques

We propose method and tool for the detection and automated refactoring of clones. We use a set of metrics to determine the impact of the applied refactorings to the maintainability of the systems. These metrics are system size, cyclomatic complexity, duplication and number of method parameters. On basis of these results, we decide which clones improve system design and thus should be refactored. We identified a set of four factors that influence the maintainability impact of clones. The first is the size of the clone. The second is the relation between the code fragments in a clone. The third is whether the clone fragments create, modify or return data. The fourth is the amount of data that cloned fragments use. By using these four factors, we can suggest only clones that will improve maintainability when refactored and prioritize them accordingly.

@@

@@

\subsection{Refactoring techniques}
In this section, we describe
Extract method, move method.

>>>>

In this study, we define a technique to detect clones such that they can be refactored. We propose a tool to detect such clones and automatically refactor a subset of them. We use a set of metrics to determine the impact of the applied refactorings to the maintainability of the systems. These metrics are system size, cyclomatic complexity, duplication and number of method parameters. On basis of these results, we decide which clones improve system design and thus should be refactored. We identified a set of four factors that influence the maintainability impact of clones. The first is the size of the clone. The second is the relation between the code fragments in a clone. The third is whether the clone fragments create, modify or return data. The fourth is the amount of data that cloned fragments use. By using these four factors, we can suggest only clones that will improve maintainability when refactored and prioritize them accordingly.

@@

In this study, we define a technique to detect clones such that they can be refactored. We evaluate the context of clones to determine refactoring techniques are required to refactor clones in a specific context. We propose a tool for the automated refactoring of a subset of the detected clones, by extracting a new method out of duplicated code.

@@

\subsection{Refactoring techniques}
In this section, we describe refactoring techniques that are relevant to refactoring code clones.

\subsubsection{Extract Method}
The most used technique to refactor duplicate code is ``Extract Method'' \cite{fowler2018refactoring}, which can be applied on code inside the body of a method. Several studies have already concluded that most duplication in source code is found in the body of methods \cite{lozano2007evaluating, white2016deep, bergman2004ethnographic}. The ``Extract Method'' technique moves functionality in method bodies to a new method. To reduce duplication, we extract the contents of a single clone instance to a new method and replace all clone instances by a call to this method.

\subsubsection{Move Method}
Often, ``Extract Method'' alone is not enough to refactor clones. This is because the extracted method has to be moved to a location that is accessible by all clone instances. To do this, we apply the ``Move Method'' refactoring technique \cite{fowler2018refactoring}. In object-oriented programming languages, we often move methods up in the inheritance structure of classes, also called ``Pull Up Method'' \cite{fowler2018refactoring}.
